### 2019-01-13 papers/journal/related.tex
SAT SMT table update

One of the prominent areas of application of SAT/SMT solvers are modeling and understanding the gene regulatory networks (GNR)~\cite{giacobbe2015model,rosenblueth2014inference, batt2010efficient, yordanov2016method, dunn2014defining, paoletti2014analyzing, koksal2013synthesis}.
%
The gene regulatory network question is encoded into a Boolean satisfiability problem and then with the help of a SAT and SMT solvers solve the generated formula. 
% 
We have extended the application of SAT and SMT solvers to a more complex biological transport network~\cite{mani2016stacking} namely vesicle traffic system.

>>>>

One of the prominent areas of application of SAT/SMT solvers are modeling and understanding the gene regulatory networks (GNR)~\cite{giacobbe2015model,rosenblueth2014inference, batt2010efficient, yordanov2016method, dunn2014defining, paoletti2014analyzing, koksal2013synthesis}.
%
The gene regulatory network question is encoded into a Boolean satisfiability problem and then with the help of a SAT and SMT solvers solve the generated formula. 
% 
We have extended the application of SAT and SMT solvers to a comparatively more complex biological transport network~\cite{mani2016stacking} namely vesicle traffic system.
